Convex Surrogates via Polyhedral Losses

### 2019-05-08 notes/bo-separated.tex
comments to bo

Let the ``thickening'' $B(T,\epsilon)$ be defined as
  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) \leq \epsilon \} . \]

@@

\begin{lemma} \label{lemma:U-biject}
  There is a bijection between $\mathcal{S}$ and $\mathcal{U}$ where $R \leftrightarrow U$ if and only if $\gamma(p) = R$ and $\Gamma(p) = U$ for some $p$.
  In this case $U$ contains $u_r$ if and only if $r \in R$.
\end{lemma}
\begin{proof}
  \bo{TODO!}
\end{proof}

@@

%% Bo: I thought this might be useful, but guess not.
%\begin{lemma}
%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
%  If $u \not\in \cap_j U_j$, then for all small enough $\epsilon > 0$, $u \not\in \cap_j B(U_j,\epsilon)$.
%\end{lemma}
%\begin{proof}
%  Consider the collection $\{U_j : j \in \mathcal{J}\}$ and suppose $u \not \in \cap_j U_j$.
%  In particular, there exists some $U$ in the collection such that $u \not\in U$.
%  Because $U$ is closed and convex, that there exists $\epsilon' > 0$ such that $d(U,u) \geq \epsilon'$.
%  So for all $\epsilon < \epsilon'$, we have $u \not\in B(U,\epsilon)$.
%  This implies $u \not\in \cap_j B(U_j,\epsilon)$.
%\end{proof}
%
\begin{lemma} \label{lemma:thick-int}
  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
\end{lemma}
\begin{proof}
  By induction on the size of the collection.
  If the size is $1$, set $\epsilon = \delta$.
  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
  There are two cases.
  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.

@@

  We now take the minimum over these finitely many $\epsilon$s (one per halfspace).
\end{proof}

@@

\begin{lemma} \label{lemma:distance-loss}
  If $L$ is a polyhedral loss, there exists a constant $c$ such that:
  For any $p$, if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
\end{lemma}
\begin{proof}
  \bo{TODO}
\end{proof}

>>>>

\raf{I think we'll want open balls, so $< \epsilon$, just because we'll get better bounds that way (larger $\epsilon$ is better).}
Let the ``thickening'' $B(T,\epsilon)$ be defined as
  \[ B(T,\epsilon) = \{u \in \R' : d(T,u) \leq \epsilon \} . \]

@@

\begin{lemma} \label{lemma:U-biject}
  There is a bijection between $\mathcal{S}$ and $\mathcal{U}$ where $R \leftrightarrow U$ if and only if $\gamma(p) = R$ and $\Gamma(p) = U$ for some $p$.
  In this case $U$ contains $u_r$ if and only if $r \in R$.
\end{lemma}
\begin{proof}
  \bo{TODO!}
  \raf{I'm not actually sure we have a bijection.  Actually, I know we don't: take hinge loss, where $\Gamma((0.9,0.1)) = \{1\}$ but $\Gamma((1,0)) = [1,\infty)$; both have $R = \{1\}$.  What we \emph{can} say is, $\mathcal{U}$ is finite, and there is a surjective map $h:\mathcal{U}\to\mathcal{S}$ where in fact $h(U) = \{r\in\R : u_r \in U\} \neq \emptyset$.  (And $u_r \in \Gamma(p) \iff r \in \gamma(p)$ of course, from embedding.)  Hopefully this is enough...}
\end{proof}

@@

%% Bo: I thought this might be useful, but guess not.
%\begin{lemma}
%  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
%  If $u \not\in \cap_j U_j$, then for all small enough $\epsilon > 0$, $u \not\in \cap_j B(U_j,\epsilon)$.
%\end{lemma}
%\begin{proof}
%  Consider the collection $\{U_j : j \in \mathcal{J}\}$ and suppose $u \not \in \cap_j U_j$.
%  In particular, there exists some $U$ in the collection such that $u \not\in U$.
%  Because $U$ is closed and convex, that there exists $\epsilon' > 0$ such that $d(U,u) \geq \epsilon'$.
%  So for all $\epsilon < \epsilon'$, we have $u \not\in B(U,\epsilon)$.
%  This implies $u \not\in \cap_j B(U_j,\epsilon)$.
%\end{proof}
%
\begin{lemma} \label{lemma:thick-int}
  Let $\{U_j : j \in \mathcal{J}\}$ be a finite collection of closed, convex sets.
  For any $\delta > 0$, there exists an $\epsilon > 0$ such that
  \[ \cap_j B(U_j,\epsilon) \subseteq B\left(\cap_j U_j, \delta\right)  \]
  where if $\cap_j U_j = \emptyset$, we interpret the right-hand side as $\emptyset$.
\end{lemma}
\begin{proof}
  \raf{Maybe cleaner to break into to two parts right off the bat: $\cap U_j$ is empty or not?}
  By induction on the size of the collection.
  If the size is $1$, set $\epsilon = \delta$.
  If the size is larger than $1$, let $U_j$ be any member of the collection, let $U' = \cap_{j'\neq j} U_{j'}$, and let $C(\epsilon) = \cap_{j' \neq j} B(U_{j'},\epsilon)$.
  There are two cases.
  If $U_j \cap U' = \emptyset$, then we must show that $B(U_j,\epsilon) \cap C(\epsilon) = \emptyset$.
  Because $U_j,U'$ are both closed and convex, they are separated by some nonzero distance. So for some $\gamma > 0$, we have $B(U_j,\gamma) \cap B(U',\gamma) = \emptyset$.
  By inductive assumption, for all small enough $\epsilon$, $C(\epsilon) \subseteq B(U',\gamma)$, so we have $B(U_j,\gamma) \cap C(\epsilon) = \emptyset$.
  Choosing a small enough $\epsilon$ that is also less than $\gamma$ completes this case.

@@

  We now take the minimum over these finitely many $\epsilon$'s (one per halfspace).
\end{proof}

@@

\begin{lemma} \label{lemma:distance-loss}
  If $L$ is a polyhedral loss, there exists a constant $c$ such that:
  For any $p$, if the set $U$ is optimal with expected loss $z$, and $d(U,u) \geq \delta$, then $L(u;p) > z + c\delta$.
\end{lemma}
\begin{proof}
  \bo{TODO}
  \raf{My first thought was ``This is a great lemma!'' but I don't think it's quite true.  Again think of hinge, and take $p\to 0.5$ from above; $U = \{1\}$ the whole time, but $L(-1,p) \to L(1,p)$, so no constant $c$ will work.  We will want a lemma like this, but I think we'll want to relate $\ell$ differences to $L$ differences, especially since that's the new definition of separated link anyway.  (Note that this more nuanced version holds for this hinge example: yes $L(-1,p)$ is getting closer to $L(1,p)$, but so is $\ell(-1,p)$ to $\ell(1,p)$.}
\end{proof}
